Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-10-18 Manuscript/manuscript.tex
Updates to the results and discussion

\begin{table}
  \caption{The relative surface excess and the probabilities of contacts between bound Calcium and different
    oxygen moieties in POPC from different simulation models. The CaCl$_2$ concentration of the ions in water
    is 350mM in the analyzed systems\label{tab:binding} }
  \begin{tabular}{l|c c c}
    model                 & $\Gamma_{Ca}^w$ (nm$^{-2}$)   & $P^\mathrm{Ca^{2+}} _\mathrm{PO_4} $ & $P^\mathrm{Ca^{2+}} _\mathrm{O_{carb.}} $ \\
    \hline
    ECC-lipids            &  $0.07 \pm 0.01 $            &  99\%   &    25\%    \\
    Lipid14/\AA{}qvist    &  $0.13 \pm 0.01 $            &  -       &     -       \\
    Lipid14/Dang          &  $ 0.3 \pm 0.03  $           &  -        &    -       \\
  \end{tabular}
\end{table}
The binding affinities of Ca$^{2+}$ ions to POPC bilayer in different simulation 
models were quantified by calculating the relative surface excess using Eq.~\ref{surfexcess} 
and the bulk concentrations determined from the density profiles in Fig.~\ref{fig:cacl-dens}. 
All these simulation have the same, $350\,\mathrm{mM}$, concentration of CaCl$_2$ with 
respect to water (concentration before solvating the lipids in experiments).
As expected from the changes of the lipid headgroup order parameters in Fig. \ref{fig:delta_ordPar_CaCl}, 
the relative surface excess for the ECC-lipid model, $\Gamma_{\rm Ca}^w = 0.07 \pm 0.01 \rm{nm}^{-2}$,
is significantly smaller than for the Lipid14 model with \AA{}qvist ions, $\Gamma_{\rm Ca}^w = 0.13 \pm 0.01 \rm{nm}^{-2}$,
or with Dang ions, $\Gamma_{\rm Ca}^w = 0.3 \pm 0.03 \rm{nm}^{-2}$.
\todo{JOE: I'd put the $\Gamma$ values into a table SAMULI: They are now in the table \label{tab:binding} 
together with probabilities of the calcium binding probabilities to different POPC oxygens. 
However, I am not sure if there the table is useful in the end.}
Interestingly, the relative surface excess of 
\ce{NaCl} at $1\,\mathrm{M}$ concentration (ECC-ions~\cite{Pluharova2014}) 
calculated using density profiles in Fig.~\ref{fig:nacl-dens}
is qualitatively different from \ce{CaCl2}
having a negative value $\Gamma_i^w = -0.1 \pm 0.01 \rm{nm}^{-2}$, 
meaning that water molecules are preferred to sodium and chloride ions at the membrane-water interface. 
This is in contrast to the most of the available lipid force fields,
which predict a specific binding of sodium on 
PC lipid bilayers \cite{catte16}.
%\todo{JOE: Add references to NaCl simulation papers that show peaks.
%Add a simple note that there is NBFIX trick in Charmm36 (?).} 
%SAMULI: I think that it is enough to cite NMRlipids II here, which shows all the results
%
%This finding is depicted in Figures~\ref{fig:nacl-dens} and~\ref{fig:cacl-dens},
%which show the density profile of ions and water along the membrane normal. 
%
%The density profiles show
%a larger Ca$^{2+}$ density peak in lipid headgroup region for
%the Lipid14 model with Dang and ECC-ions than for the ECC-lipid model.
\todo{Densities and relative surface excess from NaCl systems to be added.
  The discussion above to be finished after this.}

@@

The interactions between 
%\ce{Ca^{2+}} 
ions and different oxygen moieties of POPC,
%$\Sigma ^\mathrm{Ca^{2+}} _\mathrm{O}$,
were analyzed by calculating the probability of the
contacts with the smaller or equal distance than $0.3 \, \mathrm{nm}$, 
as done previously in Ref.~\citenum{javanainen17}. 
The results are shown in Table \ref{tab:binding}.
%
%SAMULI: I commented out the average number of contacts. All the essential information
%for this is in the probabilities.
%
%In contrast to sodium, the dominant contribution
%to the binding of \ce{Ca^{2+}} to POPC membranes comes from the phosphate group. 
%% Numbers from simulation with 346mM conc. CaCl2
%The average number of contacts per lipid 
%between \ce{Ca^{2+}} at $290\,\mathrm{mM}$ concentration and any oxygen atom in POPC is 
%$\Sigma ^\mathrm{Ca^{2+}} _\mathrm{O} = 0.134 $,    % = 17.1/128 
%whereas if only phosphate oxygen atoms are considered 
%the average number of contacts decreases only by a tiny amount to 
%$\Sigma ^\mathrm{Ca^{2+}} _\mathrm{PO_4} = 0.133 $,    % = 17.0/128 . 
%and if only carbonyl oxygen atoms are considered 
%%(phosphate oxygens contribute, but are not counted as contacts),
%this value is merely
%$\Sigma ^\mathrm{Ca^{2+}} _\mathrm{O_{carb.}} = 0.033 $.    % = 4.3/128 . 
%
% Numbers from simulation with 980/845mM conc. CaCl2
%The average number of contacts per lipid between \ce{Ca^{2+}} and any oxygen atom in POPC is 
%$\Sigma ^\mathrm{Ca^{2+}} _\mathrm{O} = 0.264 $,    % = 33.8/128 
%whereas if only phosphate oxygen atoms are considered 
%the average number of contacts decreases only by a tiny amount to 
%$\Sigma ^\mathrm{Ca^{2+}} _\mathrm{PO_4} = 0.262 $,    % = 33.5/128 . 
%and if only carbonyl oxygen atoms are considered 
%(phosphate oxygens contribute, but are not counted as contacts),
%this value is merely
%$\Sigma ^\mathrm{Ca^{2+}} _\mathrm{O_{carb.}} = 0.066 $.    % = 8.4/128 . 
The probability for the bound Ca$^{2+}$ ions to be in contact with the phosphate oxygens
is 99\%, indicating the interactions of Calcium ions purely with carbonyl oxygens has the probability of
less than 1\%. However, the probability for the bound Ca$^{2+}$ ion to be in contact with
carbonyl oxygen is 25\%, indicating that roughly quarter of the bound Calcium ions are in close contact
with both, phosphase and carbonyl oxygens. It should be noted that in this analysis carbonyl and
phospate may or may not belong to the same lipid, and the carbonyl chain locate in either of the 
acyl chains. While the higher concentrations of \ce{CaCl2} naturally increased the amount of contacts per lipid,
%for $850\,\mathrm{mM}$ concentration of \ce{CaCl2}
%the average number of contacts per lipid is increased to
%$\Sigma ^\mathrm{Ca^{2+}} _\mathrm{O} = 0.264 $, 
the distribution of contacts between phosphate and carbonyl oxygens was not affected.
The most likely contacts between Ca$^{2+}$ ions and phosphate oxygens is visualized with
the probability isodensity contours in Fig.~\ref{fig:volmaps}.
%and density profiles of ions and water along the membrane normal in Fig.~\ref{fig:cacl-dens}.

@@

Even thought the \ce{Na+} ions bind to POPC bilayer with the very low probability,
it is possible to analyze the distribution of contacts from simulations with a large
sodium concetration of $1000\,mM$.
%the average number of contacts per lipid with any oxygen atom in POPC is 
%$\Sigma ^\mathrm{Na^{+}} _\mathrm{O} = 0.106 $,    % = 17.1/128 
%whereas if only phosphate oxygen atoms are considered 
%this number decreases to 
%$\Sigma ^\mathrm{Na^{+}} _\mathrm{PO_4} = 0.085 $,    % = 17.0/128 . 
%and if only carbonyl oxygen atoms are counted 
%it is even lower, 
%$\Sigma ^\mathrm{Na^{+}} _\mathrm{O_{carb.}} = 0.048 $.    % = 4.3/128 . 
The results show that the sodium ions bind purely to the phosphate oxygens 
of POPC with the probability of 55\% and purely to the carbonyl oxygens
with the probability of 20\%, leaving the probability of 25\% for the
simultaneous binding to both, phosphate and carbonyl oxygens.  
%This is in line with the calculated negative value of 
%relative surface excess of sodium with respect to water, $\Gamma_i^w$, and
%their density profiles along the membrane normal (Fig.~\ref{fig:nacl-dens})
%suggesting that the populations of bound sodium cations 
%naturally decrease with the decreasing density of water.

In conclusion, the results suggest that the Calcium ions specifically bind to phosphate
oxygens, while occasionally interacting also with carbonyls. This is in good agreement
with the previous conclusions based in large amount of experimental and theoretical
studies \cite{hauser76,hauser78,herbette84,cevc90,binder02}, but slightly updates the
picture given by the previous MD simulation, where the binding to carbonyls was found
to be more pronounced \cite{bockmann03,bockmann04,melcrova16,javanainen17}.
Also the Sodium ions bind most likely to the phosphate oxygens, while the probability
of binding purely to carbonyls is also significant. The physiological relevance
of the details of sodium binding is, however, uncertain due to the very weak binding.

@@

The previous interpretation of the experimental data for the changes of lipid headgroup
order parameters, shown in Fig. \ref{fig:delta_ordPar_CaCl}, concluded that
the experimental data was best explained by the ternary complex binding model, 
where \ce{Ca^{2+}} ion bind to a POPC membrane with a stoichiometry 2~POPC:1~\ce{Ca^{2+}}~\cite{altenbach84}.
However, also a Langmuir adsorption model (i.e. stoichiometry 1~POPC:1~\ce{Ca^{2+}}) 
was successfully fit to the experimental data when only low concentrations of \ce{CaCl2} were considered~\cite{macdonald87}.
These binding models and the measured headgroup order parameter changes
are also inluded in the tabulated experimental binding constants~\cite{marsh13}.

Since the experimentally measured changes of the POPC lipid headgroup order parameters
as a function of CaCl$_2$ concentration are reproduced by the ECC-lipid model,
it can be used to give more versatile interepration of binding stoichiometry than
the simple binding models. The stoichiometry was directly evaluated from simulations
by calculating the relative propensities of various \ce{Ca^{2+}}:$n\times$POPC complexes,
which were defined to occur when cations and lipids were found within a cut off distance of $0.3\,\mathrm{nm}$. 
The observed propensities of
$42\%$ for two lipids,
$30\%$ for one lipid, and
$28\%$ for three lipids 
are shown in Figure~\ref{fig:cacl_complexes} for \ce{Ca^{2+}}:$n\times$POPC complexes at 285~mM concetration.
\todo{Also the larger complexes were analysed, right? So we can write ''Larger complexes were not existent in simulation.'', or something like that?}
While the ternary complex had the largest propensity,
the complexes with 1~and 3~lipids occur with only a slightly lower probability,
suggesting more complex binding stoichiometry than the simple ternary complex model.
%The symmetry of the distribution of complexes,
%from simulation as shown in Figure~\ref{fig:cacl_complexes} --   
%i.e.,
It should be, however, noted that on average one Calcium binds roughly to two lipids,
because the probabilities of forming the complexes with 1 or 3 lipids are almost equal.  
This probably explains the successfull fit of the ternary complex model to the
experimental data. 
\todo{I think that we either have to do the analysis in SI properly,
  i.e., using the real $C_I$ from simulations or remove the sentence below and
the related concent from SI.}
Ternary complex model also provides a good fit 
to our simulations with ECC-lipids 
(see Fig.~\ref{fig:cacl-bind} in SI and its caption for details). 
\begin{figure}[tbp]
  \centering
  \includegraphics[width=6.0cm]{../Fig/ipython_nb/stoichiometry_NaCl-CaCl2_comparison_Ecc-lipids.pdf} \\
  \caption{\label{fig:cacl_complexes}
      Relative probabilities of existence of \ce{Na^{+}} or \ce{Ca^{2+}} complexes
      with a certain number of POPC lipids. 
      \ce{Na^{+}} complexes were evaluated from the simulation with 1~M concentration;
      and \ce{Ca^{2+}} complexes were evaluated from the simulation with 287~mM concentration.
  }
\end{figure}

Also the probabilities of different complexes formed by \ce{Na+} ions and POPC
analyzed from the ECC-lipid model simulation with 1 M concentration of NaCl are
shown in Fig.~\ref{fig:cacl_complexes}. In contrast to Calcium, the Sodium ions
most likely binds to one POPC, while the probability to bind two lipids is less likely
and very small for more than two.
%follows stoichiomtetry \ce{Na^{+}}:$1\times$POPCas shown in

@@

The residence time of \ce{Ca^{2+}} in a POPC membrane 
is experimentally estimated to be lower than $10\,\mu\mathrm{s}$~\cite{altenbach84}.
The recent MD simulations indicate that the equilibration of \ce{Ca^{2+}}
binding to POPC bilayer may take hundreds of nanoseconds~\cite{javanainen17},
which could become an issue for the detailed binding studies with MD simulation
trajectories with the having lenght less than several microseconds \cite{catte16}.

>>>>

\begin{table}
  \caption{The relative surface excess and the probabilities of contacts between bound Calcium and different
    oxygen moieties in POPC from different simulation models. The CaCl$_2$ concentration of the ions in water
    is 350mM in the analyzed systems. \label{tab:binding}}
  \begin{tabular}{l|c c c}
    model                 & $\Gamma_{Ca}^w$ (nm$^{-2}$)   & $P^\mathrm{Ca^{2+}} _\mathrm{PO_4} $ & $P^\mathrm{Ca^{2+}} _\mathrm{O_{carb.}} $ \\
    \hline
    ECC-lipids            &  $0.07 \pm 0.01 $            &  99\%   &    25\%    \\
    Lipid14/\AA{}qvist    &  $0.13 \pm 0.01 $            &  -       &     -       \\
    Lipid14/Dang          &  $ 0.3 \pm 0.03  $           &  -        &    -       \\
  \end{tabular}
\end{table}

The binding affinities of Ca$^{2+}$ ions to POPC bilayer in different simulation 
models were quantified by calculating the relative surface excess using Eq.~\ref{surfexcess} 
and the bulk concentrations determined from the density profiles in Fig.~\ref{fig:cacl-dens}. 
All these simulation have the same, $350\,\mathrm{mM}$, concentration of CaCl$_2$ with 
respect to water, i.e., the concentration before solvating the lipids in experiments.
As expected from the changes of the lipid headgroup order parameters in Fig. \ref{fig:delta_ordPar_CaCl}, 
the relative surface excess for the ECC-lipid model, $\Gamma_{\rm Ca}^w = 0.07 \pm 0.01 \rm{nm}^{-2}$,
is significantly smaller than for the Lipid14 model with \AA{}qvist ions, $\Gamma_{\rm Ca}^w = 0.13 \pm 0.01 \rm{nm}^{-2}$,
or with Dang ions, $\Gamma_{\rm Ca}^w = 0.3 \pm 0.03 \rm{nm}^{-2}$.
\todo{JOE: I'd put the $\Gamma$ values into a table SAMULI: They are now in the table \ref{tab:binding} 
together with probabilities of the calcium binding probabilities to different POPC oxygens. 
However, I am not sure if the table is useful in the end.}
Interestingly, the relative surface excess of 
\ce{NaCl} at $1\,\mathrm{M}$ concentration (ECC-ions~\cite{Pluharova2014}) 
calculated using density profiles in Fig.~\ref{fig:nacl-dens}
is qualitatively different from \ce{CaCl2}
having a negative value $\Gamma_i^w = -0.1 \pm 0.01 \rm{nm}^{-2}$, 
meaning that water molecules are preferred to sodium and chloride ions at the membrane-water interface. 
This is in contrast to the most of the available lipid force fields,
which predict a specific binding of sodium on 
PC lipid bilayers \cite{catte16}.
%\todo{JOE: Add references to NaCl simulation papers that show peaks.
%Add a simple note that there is NBFIX trick in Charmm36 (?).} 
%SAMULI: I think that it is enough to cite NMRlipids II here, which shows all the results
%
%This finding is depicted in Figures~\ref{fig:nacl-dens} and~\ref{fig:cacl-dens},
%which show the density profile of ions and water along the membrane normal. 
%
%The density profiles show
%a larger Ca$^{2+}$ density peak in lipid headgroup region for
%the Lipid14 model with Dang and ECC-ions than for the ECC-lipid model.
\todo{Densities and relative surface excess from NaCl systems to be added.
  The discussion above to be finished after this.}

@@

The probabilities for a bound \ce{Ca^{2+}} ion to interact with
different oxygen moieties of POPC 
%$\Sigma ^\mathrm{Ca^{2+}} _\mathrm{O}$,
were analyzed by counting the contacts within the distance of $0.3 \, \mathrm{nm}$, 
as done previously in Ref.~\citenum{javanainen17}. 
%
%SAMULI: I commented out the average number of contacts. All the essential information
%for this is in the probabilities.
%
%In contrast to sodium, the dominant contribution
%to the binding of \ce{Ca^{2+}} to POPC membranes comes from the phosphate group. 
%% Numbers from simulation with 346mM conc. CaCl2
%The average number of contacts per lipid 
%between \ce{Ca^{2+}} at $290\,\mathrm{mM}$ concentration and any oxygen atom in POPC is 
%$\Sigma ^\mathrm{Ca^{2+}} _\mathrm{O} = 0.134 $,    % = 17.1/128 
%whereas if only phosphate oxygen atoms are considered 
%the average number of contacts decreases only by a tiny amount to 
%$\Sigma ^\mathrm{Ca^{2+}} _\mathrm{PO_4} = 0.133 $,    % = 17.0/128 . 
%and if only carbonyl oxygen atoms are considered 
%%(phosphate oxygens contribute, but are not counted as contacts),
%this value is merely
%$\Sigma ^\mathrm{Ca^{2+}} _\mathrm{O_{carb.}} = 0.033 $.    % = 4.3/128 . 
%
% Numbers from simulation with 980/845mM conc. CaCl2
%The average number of contacts per lipid between \ce{Ca^{2+}} and any oxygen atom in POPC is 
%$\Sigma ^\mathrm{Ca^{2+}} _\mathrm{O} = 0.264 $,    % = 33.8/128 
%whereas if only phosphate oxygen atoms are considered 
%the average number of contacts decreases only by a tiny amount to 
%$\Sigma ^\mathrm{Ca^{2+}} _\mathrm{PO_4} = 0.262 $,    % = 33.5/128 . 
%and if only carbonyl oxygen atoms are considered 
%(phosphate oxygens contribute, but are not counted as contacts),
%this value is merely
%$\Sigma ^\mathrm{Ca^{2+}} _\mathrm{O_{carb.}} = 0.066 $.    % = 8.4/128 . 
The results in Table \ref{tab:binding} show that almost all (99\%) of the 
bound Ca$^{2+}$ ions are in contact with the phosphate oxygens and a quarter
of them (25\%) interacts with the carbonyl oxygens. Thus, the interactions between
Calcium ions with only carbonyl oxygens are very unlikely (1\%), but significant
amount of the ions interact with both, phosphate and carbonyl oxygens.
The individual lipids or acyl chains were not identified in the analysis,
thus the ion contacts with both oxygen moieties may be inter or intra molecular
and occur with the carbonyls in the either of the acyl chains.
The most likely contacts between Ca$^{2+}$ ions and phosphate oxygens is visualized with
the probability isodensity contours in Fig.~\ref{fig:volmaps}.
While the higher concentrations of \ce{CaCl2} naturally increased the amount of contacts per lipid,
%for $850\,\mathrm{mM}$ concentration of \ce{CaCl2}
%the average number of contacts per lipid is increased to
%$\Sigma ^\mathrm{Ca^{2+}} _\mathrm{O} = 0.264 $, 
the distribution of contacts between phosphate and carbonyl oxygens was not affected.
%and density profiles of ions and water along the membrane normal in Fig.~\ref{fig:cacl-dens}.

@@

Even thought \ce{Na+} ions bind to POPC bilayer with a very low probability,
it was possible to analyze the distribution of contacts from simulations with a large
sodium concetration of~1\,M.
%the average number of contacts per lipid with any oxygen atom in POPC is 
%$\Sigma ^\mathrm{Na^{+}} _\mathrm{O} = 0.106 $,    % = 17.1/128 
%whereas if only phosphate oxygen atoms are considered 
%this number decreases to 
%$\Sigma ^\mathrm{Na^{+}} _\mathrm{PO_4} = 0.085 $,    % = 17.0/128 . 
%and if only carbonyl oxygen atoms are counted 
%it is even lower, 
%$\Sigma ^\mathrm{Na^{+}} _\mathrm{O_{carb.}} = 0.048 $.    % = 4.3/128 . 
The results show that the sodium ions bind purely to the phosphate oxygens 
of POPC with the probability of 55\% and purely to the carbonyl oxygens
with the probability of 20\%, leaving the probability of 25\% for the
simultaneous binding to both, phosphate and carbonyl oxygens.  
%This is in line with the calculated negative value of 
%relative surface excess of sodium with respect to water, $\Gamma_i^w$, and
%their density profiles along the membrane normal (Fig.~\ref{fig:nacl-dens})
%suggesting that the populations of bound sodium cations 
%naturally decrease with the decreasing density of water.

In conclusion, the results suggest that the Calcium ions specifically bind to phosphate
oxygens, while occasionally interacting also with carbonyls. This is in good agreement
with the previous conclusions from several experimental and theoretical
studies~\cite{hauser76,hauser78,herbette84,cevc90,binder02}, but
suggests lower relative binding affinity to carbonyls than the previous MD simulation
studies~\cite{bockmann03,bockmann04,melcrova16,javanainen17}.
Also the Sodium ions bind most likely to the phosphate oxygens, while the probability
of binding purely to carbonyls is also significant, in contrast to Calcium ions.
The physiological relevance of the Sodium binding details is, however, uncertain
due to the very weak binding affinity.

@@

The same experimental data for the lipid headgroup order parameters
used in this work to validate the simulation models in Fig. \ref{fig:delta_ordPar_CaCl},
has been previous interpreted by using simple binding models to determine the
binding constants and stoichimetry of \ce{Ca^{2+}} binding to PC lipid
bilayers~\cite{altenbach84,macdonald87}. The experimental data was best
explained by the ternary complex binding model with a binding
stoichiometry of one \ce{Ca^{2+}} per two POPC lipids~\cite{altenbach84}.
However, also a Langmuir adsorption model (i.e. \ce{Ca^{2+}}:POPC stoichiometry of 1:1) 
was successfully fit to the experimental data when only low concentrations of \ce{CaCl2} were considered~\cite{macdonald87}.
The results based on these binding models and the measured headgroup order parameter changes
are also inluded in the tabulated experimental binding constants~\cite{marsh13}.

Since the experimentally measured changes of the POPC lipid headgroup order parameters
as a function of CaCl$_2$ concentration are reproduced by the ECC-lipid model,
it can be used to give a more versatile interepration of the binding stoichiometry than
the previously used simple binding models. To directly evaluate the
stoichiometry from simulations we calculated the relative propensities of \ce{Ca^{2+}}:POPC
complexes with various stoichiometries by counting the individual lipid
molecules within the distance of $0.3\,\mathrm{nm}$ from each \ce{Ca^{2+}} ion.
The results from POPC simulation with 285~mM concetration of CaCl$_2$ in
Fig.~\ref{fig:cacl_complexes} show the largest propensity (42\%) for the
ternary complex with the \ce{Ca^{2+}}:POPC stoichiometry of 1:2, but 
the probabilities for the complexes with stoichimetries of 1:1~(30\%)~and
1:3~(28\%)~are only slightly lower,
suggesting more complex binding stoichiometry than the simple ternary complex model.
%The observed propensities of
%$42\%$ for two lipids,
%$30\%$ for one lipid, and
%$28\%$ for three lipids 
\todo{Also the larger complexes were analysed, right? So we can write ''Larger complexes were not existent in simulation.'', or something like that?}
%The symmetry of the distribution of complexes,
%from simulation as shown in Figure~\ref{fig:cacl_complexes} --   
%i.e.,
However, one Calcium binds roughly to two lipids on average also in simulations,
because the probabilities of forming the complexes with 1 or 3 lipids are almost equal.  
This probably explains the successfull fit of the ternary complex model to the
experimental data. 
\todo{I think that we either have to do the analysis in SI properly,
  i.e., using the real $C_I$ from simulations or remove the sentence below and
the related concent from SI.}
Ternary complex model also provides a good fit 
to our simulations with ECC-lipids 
(see Fig.~\ref{fig:cacl-bind} in SI and its caption for details). 
\begin{figure}[tbp]
  \centering
  \includegraphics[width=6.0cm]{../Fig/ipython_nb/stoichiometry_NaCl-CaCl2_comparison_Ecc-lipids.pdf} \\
  \caption{\label{fig:cacl_complexes}
      Relative probabilities of existence of \ce{Na^{+}} or \ce{Ca^{2+}} complexes
      with a certain number of POPC lipids. 
      \ce{Na^{+}} complexes were evaluated from the simulation with 1~M concentration;
      and \ce{Ca^{2+}} complexes were evaluated from the simulation with 287~mM concentration.
  }
\end{figure}

Also the probabilities of different complexes formed by \ce{Na+} ions and POPC
analyzed from the ECC-lipid model simulation with 1 M concentration of NaCl are
shown in Fig.~\ref{fig:cacl_complexes}. In contrast to Calcium, the
probability is largest (??\%) for 1:1 complex, significantly smaller (??\%)
for 1:2 complexes and very small (??\%) for 1:3 of \ce{Na+}:POPC complexes.
%follows stoichiomtetry \ce{Na^{+}}:$1\times$POPCas shown in 
\todo{Add numbers for Sodium.}

@@

The residence time of \ce{Ca^{2+}} in a POPC membrane 
is experimentally estimated to be lower than $10\,\mu\mathrm{s}$~\cite{altenbach84}.
\todo{This experimental estimate is actually for the residence time of Calcium
  ion at the individual PC lipid. This section is to be finished when the analysis details
and the results are here.}
The recent MD simulations indicate that the equilibration of \ce{Ca^{2+}}
binding to POPC bilayer may take hundreds of nanoseconds~\cite{javanainen17},
which could become an issue for the detailed binding studies with MD simulation
trajectories with the having lenght less than several microseconds \cite{catte16}.
